### 2016-04-20 papers/thesis-vischer/Thesis.tex
Thesis work, wrote a loose abstract Tests skipped!

\section{Introduction}
\subsection{Motivation}
Fluids have long garnered interest\cite{theorysimpleliquids}\cite{theoryofcrits}, particularly among computationally-minded researchers, as an area in which current models are unequipped to robustly predict behavior across multiple regimes. A largely troublesome \cite{white2001global} regime is near the so-called ``critical point'' where liquid and vapor are indistinguishable and, more importantly, large fluctuations of fluid density occur. Most traditional fluid models assume the density across the cell to be nearly constant. As a result, these methods tend to poorly handle these fluctuations near criticality. 
Using the well-established model of the square-well fluid, we seek to determine the applicability of a particular generalized renormalization-group (``GRG'') formalism to find the absolute Helmholtz free energy of systems near criticality.\\

@@

\begin{figure}
    \centering
    \includegraphics[width=.75\textwidth]{SWF-E.png}
    \caption{Demonstration of Square-Well approximation.}
    \label{sw_phi}
\end{figure}
\subsection{Critical Point} 
The critical point is the temperature and pressure (or any other thermodynamic pairing) on a phase diagram (shown in Figure ~\ref{phase}) where the line between liquid and vapor terminates - liquid and vapor become indistinguishable and are assimilated into the ``fluid'' phase. Many interesting effects occur here, including the well-researched phenomena of critical opalescence. The correlation length, naively interpreted here as the maximum existing wavelength of the density fluctuations within the fluid, diverges to infinity near criticality. As mentioned previously, the diverging of the correlation length invalidates SAFT and many of its variants which assume constant density. 
\begin{figure}
    \centering
    \includegraphics[width=.75\textwidth]{phase.png}
    \caption{Phase transitions of water with critical point and triple point identified.}
    \label{phase}
\end{figure}
\\
The theory of this project is largely predicated upon the behavior of critical systems, namely the phenomena of self-similarity. Non-critical systems exhibit different characteristics when viewed at different length scales. Ever-present small-scale fluctuations in density are relevant, if not dominant, when viewing the system at very small scales, but typically become less important at larger scales and nearly irrelevant near the thermodynamic limit. Near the critical point all wavelengths of fluctuation are present, and so the system looks the same regardless of length scale chosen. This self-similarity allows for the decomposition of the large critical cell to smaller constituent cells. The details of the procedure are more carefully discussed later on.

@@

Figures ~\ref{F-T} and ~\ref{F-eta} show preliminary free energy calculations.
\begin{figure}[H]
\centering
    \includegraphics[width=.75\textwidth]{ww130-L03-i1_F-T.pdf}
    \caption{Preliminary results for absolute specific free energy as a function of temperature with each quantity scaled by well depth $\epsilon$. The vertical line at $T/\epsilon = 0.3$ is the lowest temperature at which our statistics are trustworthy.}
    \label{F-T}
\end{figure}
\begin{figure}
\centering
    \includegraphics[width=.75\textwidth]{ww130-L03-F_i1_fixed_i.pdf}
    \caption{Preliminary results for free energy as a function of density.}
    \label{F-eta}
\end{figure}

>>>>

\section{Introduction}
\subsection{Motivation}
Fluids have long garnered interest\cite{theorysimpleliquids}\cite{theoryofcrits}, particularly among computationally-minded researchers, as an area in which current models are unequipped to robustly predict behavior across multiple regimes. A largely troublesome \cite{white2001global} regime is near the so-called ``critical point'' where liquid and vapor are indistinguishable and, more importantly, large fluctuations of fluid density occur. Most traditional fluid models assume the density across the cell to be nearly constant. As a result, these methods tend to poorly handle these fluctuations near criticality. 
Using the well-established model of the square-well fluid, we seek to determine the applicability of a particular generalized renormalization-group formalism (``GRG'') to find the absolute Helmholtz free energy of systems near criticality.\\

@@

\begin{figure}
    \centering
    %\includegraphics[width=.75\textwidth]{SWF-E.png}
    \caption{Demonstration of Square-Well approximation.}
    \label{sw_phi}
\end{figure}
\subsection{Critical Point} 
The critical point is the temperature and pressure (or any other thermodynamic pairing) on a phase diagram (shown in Figure ~\ref{phase}) where the line between liquid and vapor terminates - liquid and vapor become indistinguishable and are assimilated into the ``fluid'' phase. Many interesting effects occur here, including the well-researched phenomena of critical opalescence. The correlation length, naively interpreted here as the maximum existing wavelength of the density fluctuations within the fluid, diverges to infinity near criticality. As mentioned previously, the diverging of the correlation length invalidates SAFT and many of its variants which assume constant density. 
\begin{figure}
    \centering
    %\includegraphics[width=.75\textwidth]{phase.png}
    \caption{Phase transitions of water with critical point and triple point identified.}
    \label{phase}
\end{figure}
\\
The theory of this project is largely predicated upon the behavior of critical systems, namely the phenomena of self-similarity. Non-critical systems exhibit different characteristics when viewed at different length scales. Ever-present small-scale fluctuations in density are relevant, if not dominant, when viewing the system at very small scales, but typically become less important at larger scales and nearly irrelevant near the thermodynamic limit. Near the critical point all wavelengths of fluctuation are present, and so the system looks the same regardless of length scale chosen. This self-similarity allows for the decomposition of the large critical cell to smaller constituent cells. The details of the procedure are more carefully discussed later on.

@@

Figures ~\ref{F-T} and ~\ref{F-eta} show preliminary free energy calculations.
\begin{figure}[H]
\centering
    %\includegraphics[width=.75\textwidth]{ww130-L03-i1_F-T.pdf}
    \caption{Preliminary results for absolute specific free energy as a function of temperature with each quantity scaled by well depth $\epsilon$. The vertical line at $T/\epsilon = 0.3$ is the lowest temperature at which our statistics are trustworthy.}
    \label{F-T}
\end{figure}
\begin{figure}
\centering
    %\includegraphics[width=.75\textwidth]{ww130-L03-F_i1_fixed_i.pdf}
    \caption{Preliminary results for free energy as a function of density.}
    \label{F-eta}
\end{figure}

### 2016-04-20 papers/thesis-vischer/abstract.tex
Thesis work, wrote a loose abstract Tests skipped!

\thispagestyle{plain}
\begin{center}
    \Large
    \textbf{Application of Generalized Renormalization Group Methods to the Square-Well Liquid Near Criticality}

@@

You take a box, stuff it with spheres, move them around, make it bigger, do it again. Win grant.
\clearpage

>>>>

\thispagestyle{plain}
\begin{center}
    \Large
    \textbf{Application of Generalized Renormalization Group Methods to the Square-Well Liquid Near Criticality}
    \\or\\
    \textbf{Decomposition of the Critical Square-Well Liquid Into Consitutent Cells}    \\or\\
    \textbf{Free Energy Decomposition of the Critical Square-Well Liquid Using a Renormalization Group Method}

@@

The free energy of a bulk liquid is a known quantity [cite], near and far from the critical region [cite. true?]. Computing the free energy of a liquid requires lengthy, difficult computations that [something]. These computations generally involve renormalization methods which [do things]. Analytic models using renormalization methods for fluids have been [time scale] developed [cite], but computational models [something]. [something about including all lengths, not knowning what each contributes]. We present a method to determine the free energy contributions of each length scale by exploiting both the behavior of the critical fluid and the periodicity of Monte-Carlo simultations. We further detail a method by which to compute the ``absolute'' free energy, with both the ideal gas free energy and the excess free energy, for the square-well liquid. [more] We find that the square-well liquid near the critical region is well-characterized by a base cell length of $\sqrt2\sigma$, the side length of an FCC lattice.  
\clearpage
